MCC Models

### 2019-06-25 papers/full_paper/SI_appendix.Rmd
add numerical example for model
update numerical example

>>>>

### Numerical Example

P(r_1) = 0.6416667
P(r_2) = 0.3583333
SO = 2.242435

u_1 = point to table with 2 objects
u_2 = point to table with 1 object

\begin{equation} 
Informativity(u; r) = ln P(r|u) \propto ln \sum_L P(r,l|u) P(L) \propto P(r) L_{lit}
Informativity(u_1; r_1) = log(0.6416667 * 1) = -0.4436863
Informativity(u_2; r_1) = log(0.6416667 * 0) = -Inf
Informativity(u_1; r_2) = log(0.3583333 * 1) = -1.026292
Informativity(u_2; r_2) = ???? = 0
Informativity(u_1; r_3) = log(0.3583333 * ) = -Inf
Informativity(u_2; r_3) = ???? = 0

\end{equation}

\begin{equation} 
P_{S_1}(u|r)\propto exp(\alpha Informativity(u;r))
P_{S_1}(u_1|r_1) = exp(2.242435 * -0.4436863)/(exp(2.242435 * -0.4436863)) = 1
P_{S_1}(u_1|r_2) = exp(2.242435 * -1.026292)/(exp(2.242435 * -1.026292)+ exp(2.242435 * 0)) = 0.09100765
P_{S_1}(u_1|r_3) = exp(2.242435 * -1.026292)/(exp(2.242435 * -1.026292)+ exp(2.242435 * 0)) = 0.09100765 <-- Why????
\end{equation}

(For the above, I get the same results from the model if get these values from webppl)

\begin{equation} 
P_{L_1}(r,L|u)\propto P_{S_1}(u|r)P(L)P(r)
P_{L_1}(r_1,L|u) = 1 * 0.6416667 /(1*0.6416667 + 0.09100765*0.3583333 + 0.09100765*0.3583333) = 0.9077335
\end{equation}
